\section{Conclusions}
In this paper we described the extensions to Meta-Casanova that add modules and type operators.
The extensions pave the way for modular libraries with strong abstractions and leaves room for dependent types in the future.

\subsubsection*{Related Work}
To learn more about the syntax and semantics of Meta-Casanova, refer to the paper by Jarno Holstein\cite{holstein16}.
To learn about the evolution of the standard library of Meta-Casanova and its applications, refer to the paper by Louis van der Burg\cite{vanderburg16}.

For more information on Meta-Casanova, see the Meta-Casanova paper at \url{https://github.com/vs-team/Papers} or browse the freely-available source code at \url{https://github.com/vs-team/metacasanova}.

\subsubsection*{Further work}
In the immediate future there will be three bachelor theses on Meta-Casanova.
Jarno Holstein will write his bachelors thesis on the implementation of the type-checker for the typesystem with the extensions described in this paper.
Louis van der Burg will write his on the implementation and design of the Meta-Casanova library in the Meta-Casanova language.
Finally, I will write mine on the implementation of a reliable code-generator.

In the not-so-immediate future, there is the elephant in the room: full dependent types.
Although dependent types complement the TypeFunc and Module system, it does not have the priority at the moment.
The possibility for dependent types is therefore left open for future extensions.
